Checkpoint 3

### 2020-04-23 Checkpoint3.Rmd
Update Checkpoint3.Rmd

---
title: "Checkpoint 3"
author: "Quinn Rafferty, Sofia Pozsonyiova, Will Madairy, Federico Chung"
date: ""
output: 
  html_document:
    toc: true
    toc_float: true
---

@@

##Dataset Description 
**Put in Data Descriptions Here**

@@

```{r}
## Creating a df of just the cases the week before 3/17
weekbefore <- data.frame(states_cases_data) %>% filter(date <= as.Date("2020-03-17"))

@@

## Creating a df of just the cases the week after 3/17
weekafter <- data.frame(states_cases_data) %>% filter(date >= as.Date("2020-03-17"))

@@

```{r}
# 
ggplot(Finaldata, aes(x = positive, fill = StateColor)) + 
    geom_density(alpha = .8)+ ggtitle("Positive COVID-19 Cases by State Party") + xlab("Cases") + ylab("Density")+xlim(0,500)
```

```{r}
library(statebins)
plot3<-statebins(state_data = weekbefore, state_col = "state",
                     text_color = "white", value_col = "positive",
                     brewer_pal="Spectral", font_size = 3,breaks =7,
                     legend_title="Week Before",
                 labels = c("0","1-5","5-10","10-20","20-30","30-40","50-100"))

>>>>

---
title: "Checkpoint 3"
author: "Quinn Rafferty, Sofia Pozsonyiova, Will Madairy, Federico Chung"
date: "4/24/2020"
output: 
  html_document:
    toc: true
    toc_float: true
---

@@

##Dataset Description

@@

```{r}
## Creating a df of just the cases the week before 3/17
weekbefore <- data.frame(Finaldata) %>% filter(date <= as.Date("2020-03-17"))

@@

## Creating a df of just the cases the week after 3/17
weekafter <- data.frame(Finaldata) %>% filter(date >= as.Date("2020-03-17"))

@@

```{r}
# Positive COVID cases aggregated by party 
ggplot(Finaldata, aes(x = positive, fill = StateColor)) + 
    geom_density(alpha = .8)+ ggtitle("Positive COVID-19 Cases by State Party") + xlab("Cases") + ylab("Density")+xlim(0,500)
```

```{r}
## Positive COVID cases map before and after week 
library(statebins)
plot3<-statebins(state_data = weekbefore, state_col = "state",
                     text_color = "white", value_col = "positive",
                     brewer_pal="Spectral", font_size = 3,breaks =7,
                     legend_title="Week Before",
                 labels = c("0","1-5","5-10","10-20","20-30","30-40","50-100"))
